D-Hammer: Efficient Equational Reasoning for Labelled Dirac Notation

### 2025-04-11 06related_conclusion.tex
.
fix tool referenece

\section{Related Work}

@@

There are many similarities between the ZX calculus and our formalism
for Labelled Dirac notation. However, there are also some differences
between our formalism and the ones used in ZX calculus. In particular,
our language supports big operators, tensors, and various operations
on Hilbert spaces. These features are typically not considered in
prior work on the ZX calculus, and as a consequence many examples
handled by D-Hammer lack an immediate translation into ZX-calculus.
This additional generality comes with a price. On the one hand, our
theoretical results are weaker: we do not claim completeness or
minimality. Similarly, practical implementations of the ZX-calculus,
such as PyZX~\cite{kissinger2020pyzx}, outperform D-Hammer on examples
that can be handled by both tools, as shown in \Cref{sec:eval}.

>>>>

\section{Related Work}\label{sec:relwork}

@@

There are many similarities between the ZX calculus and our formalism
for Labelled Dirac notation. However, there are also some differences
between our formalism and the ones used in ZX calculus. In particular,
our language supports big operators, tensors, and various operations
on Hilbert spaces. These features are typically not considered in
prior work on the ZX calculus, and as a consequence many examples
handled by D-Hammer lack an immediate translation into ZX-calculus.
This additional generality comes with a price. On the one hand, our
theoretical results are weaker: we do not claim completeness or
minimality. Similarly, practical implementations of the ZX-calculus~\cite{kissinger2020pyzx,9868772} outperform D-Hammer on examples
that can be handled by both tools, as shown in \Cref{sec:eval}.
